Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-09 article.rnw
Replace the excuse in the model fitting methods with a better explanation, based on using per capita fecundity.

The model was fitted by least squares regression, with a normal likelihood.\footnote{
	I recognise that this is erroneous, and a likelihood directly suited to count data would be more appropriate.
	The choice to fit the Lotka--Volterra model specifically, rather than a generic regression model, prohibited the use of a link function.
	This prevented me from using the typical methods of generalised nonlinear regression, and I have not yet managed to develop the methods necessary to fit the model using a Poisson or negative binomial likelihood.
}

>>>>

The models were fitted to the data using regression techniques.
Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
As such, I assumed a normal error distribution, and fitted a least squares regression.
To prevent heteroskedasticity, I used the \emph{per capita} fecundity as the response variable, as in the following model:
\[
	\frac{N_{i,t+1}}{N_{i,t}} = r_i \left(1 - \sum_j N_j \alpha_{ij}\right)
.\]
